Homicide Increases in the COVID-19 Era

### 2025-02-27 Draft1.qmd
fixed data load

# primary dataset
crime_la <- read.csv("Cleaned_Data/all_crimes_2010_present.csv")

@@

@@

>>>>

# primary datasets
# Primary datasets: Crime Data 2020-Present and 2010-2019
crime_la_2010_2019 <- read.csv("Raw_Data/Crime_Data_from_2010_to_2019.csv")

crime_la <- read.csv("Cleaned_Data/all_crimes_2010_present.csv")

@@

# since we do not have pre- and post- pandemic city of LA data, we are instead using LA county data for evictions. 
```

@@

# Data Sources {.unnumbered}
## Primary Datasets {.unnumbered}
Crime Data From 2010-2019: https://data.lacity.org/Public-Safety/Crime-Data-from-2010-to-2019/63jg-8b9z/about_data

Crime Data From 2020-Present: https://catalog.data.gov/dataset/crime-data-from-2020-to-present

## Secondary Datasets {.unnumbered}
Los Angeles County Eviction Data: https://calmatters.org/housing/homelessness/2023/11/california-evictions-post-pandemic/

City of Los Angeles Eviction Data: https://housing.lacity.gov/residents/renters/eviction-notices-filed

Median Income Data: https://data.census.gov/table/ACSST1Y2023.S1903?q=income
